%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
% 
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{watson-cv}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Michelle}{Watson}
{ 
\urlstyle{same} 
Biomedical Engineering Candidate \\
\href{mailto:ma2watson@uwaterloo.ca}{ma2watson@uwaterloo.ca}
\hfill 
647-296-4890\\

\href{http://github.com/Michelle-Watson}{github.com/Michelle-Watson}
\hfill
\href{https://www.linkedin.com/in/michelleawatson}{in/michelleawatson}
}
\begin{minipage}[t]{0.2\textwidth}
\end{minipage}
\begin{minipage}[t]{0.8\textwidth}
\\
\vspace{50}
\large
MaRS Centre, Suite 510 \\
661 University Avenue \\
Toronto, Ontario\\
M5G 0A3\\
\\
To whom it may concern, \\

I was inspired to apply to this position after recommendation from Kunal Chandan. I’ve often thought that there is a deep chasm between computer science and biology. However, with the advances in sequencing technologies, I’ve felt increasingly inspired to contribute to this growing field.\\
\\
“Be the change you wish to see in the world”\\
-	Gandhi\\
\\
I live by this philosophy, I have taken every initiative I can through my time in high school and university to make a positive social change. From volunteering at a hospital to leading environmental and social causes, I’ve helped change and impact the lives of many in the community around me. I had the opportunity to collaborate with hundreds of students in and around the schools near me. Through workshops with elementary schools, we were able to translate and enable an environmental mindset from an early age, changing their lives for the better.\\
\\
Through high school, my deep fascination in medicine led me to pursue a coop position in postpartum care. This combined with my love for technology led me to enter biomedical engineering and continue learning about software applications to the field of medicine. From my data structures and algorithms course, I became more interested in alignment algorithms and quality control in sequencing, and even did further research into Levenshtein distances and their applications in sequencing alignment. I hope to have the opportunity to learn more alongside the brilliant minds at OICR.\\


Sincerely,\\
Michelle Watson\\
\\
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Day this will be useful, not now though
%\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}
\end{document}  \documentclass[]{article}
